---
title: 'Case Study 1: Breweries & Beer Information'
author: "Noelle Brown & Ann Nelson"
date: "October 15, 2017"
output: html_document
---
# Introduction:

*Insert Intro Here*

*Import the data sets and change the column names for consistency.*
```{r}
Beers <- read.csv("~/Documents/Git/CaseStudy1Files/Beers.csv")
Breweries <- read.csv("~/Documents/Git/CaseStudy1Files/Breweries.csv")
names(Breweries)[names(Breweries) == 'Brew_ID'] <- 'Brewery_id'
```

**1. How many breweries are present in each state?**

*insert code explanation*
*insert code chunk*
*insert answer*

**2. Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file.**

*Merge the data sets and rename column names to make readable.*
```{r, echo=TRUE}
BeersBreweries <- merge(Beers, Breweries, by='Brewery_id')
names(BeersBreweries)[names(BeersBreweries) == 'Name.x'] <- 'Beer_Name'
names(BeersBreweries)[names(BeersBreweries) == 'Name.y'] <- 'Brewery_Name'
```
*insert answer*

**3. Report the number of NA's in each column.**

*insert code explanation*
*insert code chunk*
*insert answer*

**4. Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.**

*Compute the median alcohol content & international bitterness unit for each state, renames columns for consistency, merges values; plot bar chart of each value.*
```{r, echo=TRUE, fig.width=12}
medianABVbystate <- aggregate(BeersBreweries$ABV, list(BeersBreweries$State), median, na.rm=TRUE)
names(medianABVbystate)[names(medianABVbystate) == 'Group.1'] <- 'State'
names(medianABVbystate)[names(medianABVbystate) == 'x'] <- 'MedianABV'
medianIBUbystate <- aggregate(BeersBreweries$IBU, list(BeersBreweries$State), median, na.rm=TRUE)
names(medianIBUbystate)[names(medianIBUbystate) == 'Group.1'] <- 'State'
names(medianIBUbystate)[names(medianIBUbystate) == 'x'] <- 'MedianIBU'
medianbystate <- merge(medianABVbystate, medianIBUbystate, by='State')
```
The median ABV and IBU values by state:
```{r,echo=TRUE,fig.width=12}
medianbystate
```
Barplot for median ABV by state:
```{r,echo=TRUE,fig.width=12}
barplot(medianbystate$MedianABV, main="Median ABV by State", xlab="State", ylab="ABV", col="darkblue", names.arg=medianbystate$State, las=2)
```
Barplot for median IBU by state:
```{r,echo=TRUE,fig.width=12}
barplot(medianbystate$MedianIBU, main="Median IBU by State", xlab="State", ylab="IBU", col="red", names.arg=medianbystate$State, las=2)
```

**5. Which state has the maximum alcoholic (ABV) beer? Which state has the most bitter (IBU) beer?**

*Finds the max ABV value from all states, finds state that the value belongs to, prints out just the state with the maximum value.*
```{r, echo=TRUE}
maxABV <- max(BeersBreweries$ABV, na.rm=TRUE)
maxABVstate <- BeersBreweries[BeersBreweries$ABV == maxABV, "State"]
maxABVstate <- maxABVstate[!is.na(maxABVstate)]
maxABVstate
```
The state that has the maximum alcoholic (ABV) beer is Colorado (CO).

*Finds the max IBU value from all states, finds state that the value belongs to, prints out just the state with the maximum value.*
```{r, echo=TRUE}
maxIBU <- max(BeersBreweries$IBU, na.rm=TRUE)
maxIBUstate <- BeersBreweries[BeersBreweries$IBU == maxIBU, "State"]
maxIBUstate <- maxIBUstate[!is.na(maxIBUstate)]
maxIBUstate
```
The state that has the most bitter (IBU) beer is Oregon (OR).

**6. Summary statistics for the ABV variable.**

*insert code explanation*
*insert code chunk*
*insert answer*

**7. Is there an apparent relationship between the bitterness of the beer and its alcoholic content? Draw a scatter plot.**

*insert code explanation*
*insert code chunk*
*insert answer*

# Conclusion:

*Insert Conclusion Here*