---
title: 'Case Study 1: Breweries & Beer Information'
author: "Noelle Brown & Ann Nelson"
date: "October 15, 2017"
output: html_document
---
# Introduction:

*Insert Intro Here*

Import the data sets and change the column names for consistency.
```{r}
Beers <- read.csv("~/Documents/Git/CaseStudy1Files/Beers.csv")
Breweries <- read.csv("~/Documents/Git/CaseStudy1Files/Breweries.csv")
names(Breweries)[names(Breweries) == 'Brew_ID'] <- 'Brewery_id'
```

**1. How many breweries are present in each state?**

*insert code explanation*
*insert code chunk*
*insert answer*

**2. Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file.**

Merge the data sets and rename column names to make readable.
```{r, echo=TRUE}
BeersBreweries <- merge(Beers, Breweries, by='Brewery_id')
names(BeersBreweries)[names(BeersBreweries) == 'Name.x'] <- 'Beer_Name'
names(BeersBreweries)[names(BeersBreweries) == 'Name.y'] <- 'Brewery_Name'
```
*insert answer*

**3. Report the number of NA's in each column.**

*insert code explanation*
*insert code chunk*
*insert answer*

**4. Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.**

Compute the median alcohol content & international bitterness unit for each state, renames columns for consistency, merges values; plot bar chart of each value.
```{r, echo=TRUE, fig.width=12}
medianABVbystate <- aggregate(BeersBreweries$ABV, list(BeersBreweries$State), median, na.rm=TRUE)
names(medianABVbystate)[names(medianABVbystate) == 'Group.1'] <- 'State'
names(medianABVbystate)[names(medianABVbystate) == 'x'] <- 'MedianABV'
medianIBUbystate <- aggregate(BeersBreweries$IBU, list(BeersBreweries$State), median, na.rm=TRUE)
names(medianIBUbystate)[names(medianIBUbystate) == 'Group.1'] <- 'State'
names(medianIBUbystate)[names(medianIBUbystate) == 'x'] <- 'MedianIBU'
medianbystate <- merge(medianABVbystate, medianIBUbystate, by='State')
barplot(medianbystate$MedianABV, main="Median ABV by State", xlab="State", ylab="ABV", col="darkblue", names.arg=medianbystate$State, las=2)
barplot(medianbystate$MedianIBU, main="Median IBU by State", xlab="State", ylab="IBU", col="red", names.arg=medianbystate$State, las=2)
```
*insert answer*

**5. Which state has the maximum alcoholic (ABV) beer? Which state has the most bitter (IBU) beer?**

*insert code explanation*
*insert code chunk*
*insert answer*

**6. Summary statistics for the ABV variable.**

*insert code explanation*
*insert code chunk*
*insert answer*

**7. Is there an apparent relationship between the bitterness of the beer and its alcoholic content? Draw a scatter plot.**

*insert code explanation*
*insert code chunk*
*insert answer*

# Conclusion:

*Insert Conclusion Here*